---
title: "Health_Insurance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Health_Insurance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(basmah)
```

## Primary Aim

My app lets the user explore health care insurance coverage and associate it to various health outcomes.
The users will be able to explore data series using an interactive R shiny app.

The app provides an interface to the World data bank. 
I did pre-select eight series for the users to select.
The series will include measures of health insurance, health care accessibility, health outcomes and demographic information. 
The users can select data series, graphing methods and statistical analysis.

This app helps inform policy makers and tell them how health insurance and health care availability is related to health outcomes.



## Install the app

```{r}
# install.packages("devtools")
#devtools::install_github("Basmahsal/basmah")

```


## Use the gadget

There is a sample data set called `dd` that can be used to run the app. 
You can also supply your own data set. 

The users need to specify the outcomes and the predictors as I showed below.

```{r,eval=FALSE}
library(alharbi)
library(shiny)
library(miniUI)
library(dplyr)
library(ggplot2)





outcomes <- c("SH.UHC.NOP2.ZG",
                  "SH.XPD.CHEX.PP.CD" ,
                  "SH.XPD.EHEX.PP.CD",
                  "SH.XPD.OOPC.CH.ZS")

predictors <- c("NY.ADJ.NNTY.KD.ZG" ,
                "SP.DYN.LE00.IN" ,
                "SH.XPD.PVTD.PP.CD",
                "SH.XPD.GHED.PP.CD")

myGadgetFunc(dd,outcomes, predictors)
```

